\thesistitle

### 2019-08-25 sections/introduction.tex
Introduction again

\subsection{Research method}
We perform an \textbf{exploratory} study to look into the opportunities to automatically refactor code clones. To do this, we combine knowledge from literature with our own experience to develop definitions for refactorable clones. We also develop a tool to detect, analyze and refactor such clones. Using this tool, we perform \textbf{quantitative} experiments in which we statistically collect information about duplication in open-source software. In these experiments, we control several variables to see their impact on the results. During this process, we explore concepts and develop understanding, because of which decisions in the study design are based on the results of the experiments.

\section{Contributions}
Many studies report that code clones negatively affect maintainability \cite{heitlager2007practical, monden2002software, juergens2009code, chatterji2013effects}. However, no studies yet show in what cases code clones can reduce maintainability in source code. Refactoring often includes tradeoffs between design alternatives. With some code clones, the refactored alternative is less maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}. In this study, we analyze the maintainability of refactored code clones to improve the suggestion of code clones that should be refactored. This assists with both the identification and refactoring of code clones.

\subsection{Identification}
There are many tools to detect clones. The goal of most of these tools is to assist developers in reducing duplication in their code, i.e. assisting in the refactoring process. The problem is that these tools have no insight into the impact of refactoring such clones on the maintainability of the software. In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact. If the maintainability increases after refactoring, this gives a strong indication that the clone should be refactored. This way the results of our study can support the clone identification process.

\subsection{Refactoring}
The tool that results from this research can assist in the process of applying refactorings to clones. The tool will only apply a refactoring if the clone is refactorable and the maintainability of the source code increases as a result of applying the refactoring. The tool applies only refactorings that do not, in any way, influence the functional correctness of the program. Because of this, potential bugs as a result of refactoring can be avoided \cite{bavota2012does}.

\section{Scope}
In this study, we perform research efforts to be able to detect refactorable clones. We will apply refactoring techniques to a subset of these clones and analyze the maintainability of the resulting source code.

@@

\subsection{Measuring Maintainability}
There is a lot of study on what metrics to consider to measure maintainability. In this study, we focus solely on the practical maintainability model by Heitlager et al. \cite{heitlager2007practical}. We consider the maintainability scores described in that paper as a sufficiently accurate indication of maintainability. This will be used to quantitatively determine the impact on maintainability when applying refactoring techniques to code clones.

\subsection{Naming Declarations}
Our automated refactoring tool can create new methods, classes, and interfaces when refactoring clones. Each of these declarations needs to have a name. Because the quality of the name will not have an impact on the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study. For our automated refactoring efforts, we will use generated names for these declarations. %This may decrease the usefulness of the results of this research for refactoring-assistance.

\subsection{Testcode}
It is very disputable whether unit tests are subject to the same maintainability metrics that apply to the functional code. Because of that, for this research, unit tests are not taken into scope. The findings of this research may apply to test classes, but we will not argue the validity. Furthermore, any other code than the production code of the system will not be taken into account. In Section~\ref{chap:corpus} we describe what classes we perform our experiments on.

\section{Outline}
In Chapter~\ref{ch:background} we describe the background of this thesis. In Chapter~\ref{chap:clonetypes} we list shortcomings with established clone definitions which make them less suitable for automated refactoring. We also propose a set of clone type definitions that strive to solve these shortcomings. In Chapter~\ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored. Using this tool we perform a set of experiments, of which the setup is explained in Chapter~\ref{ch:experimentalsetup}. The results of the experiments are in shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work} contains the work related to this thesis. Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.

>>>>

\subsection{Research method}
We perform an \textbf{exploratory} study to look into the opportunities to automatically refactor code clones. To do this, we combine knowledge from literature with our own experience to develop definitions for refactorable clones. We also develop a tool to detect, analyze, and refactor such clones. Using this tool, we perform \textbf{quantitative} experiments in which we collect statistical information about duplication in open-source software. In these experiments, we control several variables to see their impact on the results. During this process, we explore concepts and develop understanding, because of which decisions in the study design are based on the results of the experiments.

\section{Contributions}
Many studies report that code clones negatively affect maintainability \cite{heitlager2007practical, monden2002software, juergens2009code, chatterji2013effects}. However, no studies yet show in what cases clones can reduce maintainability in source code. Refactoring often includes trade-offs between design alternatives. With some clones, the refactored alternative is less maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}. In this study, we analyze the maintainability of refactored clones to improve the suggestion of clones that should be refactored. This assists with both the identification and refactoring of clones.

\subsection{Identification}
There are many tools to detect clones. The goal of most of these tools is to assist developers in reducing duplication in their code, i.e. assisting in the refactoring process. The problem is that these tools have no insight into the impact of refactoring such clones on the maintainability of the software. In this study, we analyze a before- and after-refactoring snapshot of the code to determine the impact of a refactoring. If the maintainability increases after refactoring, this gives a strong indication that the clone should be refactored. This way the results of our study can support the clone identification process.

\subsection{Refactoring}
The tool that results from this research can assist in the process of applying refactorings to clones. The tool only applies a refactoring if the clone is refactorable and the maintainability of the source code increases as a result of applying the refactoring. Furthermore, the tool applies only refactorings that do not influence the functional correctness of the program. Because of this, potential bugs as a result of manual refactoring can be avoided \cite{bavota2012does}.

\section{Scope}
In this study, we perform research efforts to be able to detect refactorable clones. We apply refactoring techniques to a subset of these clones and analyze the maintainability of the resulting source code.

@@

\subsection{Measuring Maintainability}
There is a lot of study on what metrics to consider to measure maintainability. In this study, we focus solely on the practical maintainability model by Heitlager et al. \cite{heitlager2007practical}. We consider the maintainability scores described in that paper as a sufficiently accurate indication of maintainability. We use this to quantitatively determine the impact on maintainability when applying refactoring techniques to code clones.

\subsection{Naming Declarations}
Our automated refactoring tool can create new methods, classes, and interfaces when refactoring clones. Each of these declarations needs to have a name. Because the quality of the name will not have an impact on the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study. For our automated refactoring efforts, we use generated names for these declarations.

\subsection{Testcode}
It is very disputable whether unit tests are subject to the same maintainability metrics that apply to the functional code. Because of that, for this research, unit tests are not taken into scope. The findings of this research may apply to test classes, but we will not argue the validity. Furthermore, any other code than the production code of the system will not be taken into account in our experiments. In Section~\ref{chap:corpus} we describe what classes we perform our experiments on.

\section{Outline}
In Chapter~\ref{ch:background} we describe the background of this thesis. In Chapter~\ref{chap:clonetypes} we list shortcomings with established clone definitions which make them less suitable for automated refactoring. We also propose a set of clone type definitions that strive to solve these shortcomings. In Chapter~\ref{ch:clonerefactor} we propose a tool to detect, analyze, and automatically refactor such clones that can be refactored. Using this tool we perform a set of experiments, of which the setup is explained in Chapter~\ref{ch:experimentalsetup}. The results of the experiments are in shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work} contains the work related to this thesis. Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.
